KeysarMouseTracking.csv

### 2017-07-15 analysis/cogSci_analysis.Rmd
Add a bunch of hard-coded value plots for talk

```{r}
library(boot)
library(irr)
turkerRatings <- read.csv("../../normingExperiment/data/keysarNorming-trials.csv")
relevantProperties <- c("objectSet", "label")

criticalMessagesExp1 <- read.csv("../analysis/messagesExp1.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.1")
criticalMessagesExp2 <- read.csv("../analysis/messagesExp2.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.2")

@@

>>>>

```{r}
library(boot)
library(irr)
turkerRatings <- read.csv("../normingExperiment/data/keysarNorming-trials.csv")
relevantProperties <- c("objectSet", "label")

criticalMessagesExp1 <- read.csv("../experiment1/data/message/analysis/messagesExp1.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.1")
criticalMessagesExp2 <- read.csv("../analysis/messagesExp2.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.2")

@@

# Vanity plots for talk

```{r}
library(ggplot2)
library(ggthemes)
d.model <- data.frame(x = rep(c('fish', 'blue fish'), 2),
                      y = c(0.37,0.63,0.73, 0.27),
                      source = c(rep('with context-uncertainty', 2),
                                 rep('without context-uncertainty', 2)))
ggplot(d.model, aes(x=x, y=y, fill = x)) +
  geom_bar(stat='identity', position = 'dodge') +
  theme_few() +
  scale_fill_manual(values = c('red', 'grey')) +
  facet_wrap(~ source) +
  ylab("P(u | o)")
```

```{r}
d.comp <- data.frame(x = rep(c('experimental', 'baseline'), 2),
                      y = c(.30, 0, .43, .02),
                      source = c(rep('original', 2),
                                 rep('replication', 2)),
                     error = c(1/sqrt(38*4),1/sqrt(38*4), 
                               1/sqrt(14 * 4), 1/sqrt(14 * 4)))
ggplot(d.comp, aes(x=x, y=y, fill = x)) +
  geom_bar(stat='identity', position = 'dodge') +
  theme_few() +
  scale_fill_manual(values = c('red', 'grey')) +
  geom_errorbar(aes(ymin = y - error, ymax = y + error), width = 0) +
  facet_wrap(~ source) +
  ylim(0, 1) +
  ylab("% total errors")
```

```{r}
d.comp <- data.frame(x = rep(c('experimental', 'baseline'), 3),
                      y = c(.30, 0, .43, .02, .24, 0),
                      source = ordered(c(rep('original', 2),
                                 rep('Exp. 1', 2),
                                 rep('Exp. 2', 2)),
                                 levels = c('original', 'Exp. 1', 'Exp. 2')),
                     error = c(1/sqrt(38*4),1/sqrt(38*4), 
                               1/sqrt(14 * 4), 1/sqrt(14 * 4),
                               1/sqrt(32*4), 1/sqrt(32*4)))
ggplot(d.comp, aes(x=x, y=y, fill = x)) +
  geom_bar(stat='identity', position = 'dodge') +
  theme_few() +
  scale_fill_manual(values = c('red', 'grey')) +
  geom_errorbar(aes(ymin = y - error, ymax = y + error), width = 0) +
  facet_wrap(~ source) +
  ylim(0, 1) +
  ylab("% total errors")
```
